Global deaths due to air ollution

### 2022-04-30 outline.Rmd
Made changes to the slidy presentation

---
title: "rough outline"
output: slidy_presentation
date: '2022-04-25'
---

# Introduction 
* Air pollution can be detrimental to both our health and the climate
  + Pollutants of major public health concern include carbon monoxide, ozone, nitrogen oxide, and sulfur oxide
  + Outdoor and indoor air pollution cause respiratory and other diseases. 
  + Air pollution kills about 7 million people worldwide every year

* We want to look at death rates of air pollution world wide

* Why?
  + Hopefully this information can showcase the importance of air pollution and that we should be more mindful about our planet

* Overview
  + We will see how different air pollution types affect the population 
  + See if countries have implemented better techniques to reduce air pollution

@@

>>>>

---
title: "Global deaths due to air ollution"
author: "Elizabeth Bekele, Alison Cheek"
output: slidy_presentation
date: '2022-05-03'
---

# Introduction 
* Air pollution can be detrimental to both our health and the climate
  + Outdoor and indoor air pollution cause chronic pain, respiratory diseases, shortened lifespan
  + Air pollution kills about 7 million people worldwide every year 
  + Hopefully this information can showcase the importance of air pollution and that we should be more mindful about our planet

* Overview
  + We will see how different air pollution types affect the population 
  + compare past and present population numbers
  + determine which air pollutant type has the highest associated death rate

@@

# Data Details 
*Air pollution deaths 
  +Kaggle: https://www.kaggle.com/datasets/akshat0giri/death-due-to-air-pollution-19902017 
  + Author: Akshat Giri
  + Last update: 2 years ago
